---
output:
  html_document:
    keep_md: yes
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


<<<<<<< HEAD
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/fastR)](https://cran.r-project.org/package=fastR)

[![Travis-CI Build Status](https://travis-ci.org/rpruim/fastR.svg?branch=master)](https://travis-ci.org/rpruim/fastR/)
=======
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/fastR2)](http://cran.r-project.org/package=fastR2)
>>>>>>> 2e

fastR2
=======

This package contains data sets and some utility functions to support
*Foundations and Applications of Statistics: An Introduction Using R*
by Randall Pruim.

### Installation

The package can be installed from CRAN via
```{r eval=FALSE}
install.packages("fastR2")
```
or from github
```{r eval=FALSE}
devtools::install_github("rpruim/fastR")
```

### Snippets

In addtion to data sets, `fastR` contains a `snippet()` function that 
loads and executes code found in the text.  Here is an example:

```{r message=FALSE}
require(fastR2)
require(multcomp)
snippet("bugs")
```


